Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Formatting
Add rough sketch for expectations

%%%% Describe the problem.
\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            BDD approaches \emph{Test-driven development (TDD)} and
            \emph{Acceptance test-driven development (ATDD)} with a new
            terminology and mindset .  For the purpose of this paper we focus
            on the TDD aspect of BDD.
        \item
            Automating things, and continuous integration is an important
            aspect of BDD.
    \end{itemize}
\end{quote}

@@

\item[property]
    Property means a QuickCheck property as defined in~\cite{quickcheck}.

@@

\begin{quote}
    TBD:
\begin{itemize}
    \item Motivate \verb|test-shouldbe|
    \item Motivate \verb|shouldThrow|
    \item \emph{optional:} Motivate why it's important to integrate \doctest{} with
        Cabal.
    \item \emph{optional:} Motivate \verb|hspec-discover|
        It is common to have several files that contain \emph{specs}.
        And we want to be able to run them all together.  Hspec allows
        us combine specs together.  But this has to be done manually.
        Hspec does not provide a way to automatically discover and run
        all specs of a project.
\end{itemize}
\end{quote}

@@

    it "gives the original list, if applied twice" $ property $
      \xs -> reverse (reverse xs) == (xs :: [Int])
\end{verbatim}
\end{quote}

@@

\subsection{Combinators for expectations}
TBD
\subsection{Automatic discovery of specs}
TBD

>>>>

%%%% Describe the problem.
\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            BDD approaches \emph{Test-driven development (TDD)} and
            \emph{Acceptance test-driven development (ATDD)} with a new
            terminology and mindset .  For the purpose of this paper we focus
            on the TDD aspect of BDD.
        \item
            Automating things, and continuous integration is an important
            aspect of BDD.
        \item
            BDD uses expectations instead of assertions
    \end{itemize}
\end{quote}

@@

\item[expectation]
    Expectations are used to define the expected outcome of a code
    example.  They serve the same purpose as assertions in xUnit
    testing frameworks, but use a different terminology.

\item[property]
    Property means a QuickCheck property as defined in
    \cite{quickcheck}.

@@

\begin{quote}
    TBD:
\begin{itemize}
    \item Motivate \verb|test-shouldbe|

        BDD frameworks use \emph{should} or \emph{must} instead of
        \emph{assert}.

        Here is an example that uses RSpec.

        \begin{verbatim}
23.should eq(23)
        \end{verbatim}

        RSpec provides a mechanism to expect exceptions.

        \begin{verbatim}
expect {launche_missiles}.to raise_error
        \end{verbatim}

        \hspec does not yet provide a mechanism to set expectations
        about the outcome of code examples.  It uses HUnit assertions
        instead.

        HUnit does not provide a mechanism to expect exceptions.

    \item Motivate \verb|shouldThrow|
    \item \emph{optional:} Motivate why it's important to integrate \doctest{} with
        Cabal.
    \item \emph{optional:} Motivate \verb|hspec-discover|

        It is common to have several files that contain \emph{specs}.
        And we want to be able to run them all together.  Hspec allows
        us combine specs together.  But this has to be done manually.
        Hspec does not provide a way to automatically discover and run
        all specs of a project.
\end{itemize}
\end{quote}

@@

    it "gives the original list, if applied twice" $
      property $ \xs ->
        (reverse . reverse) xs == (xs :: [Int])
\end{verbatim}
\end{quote}

@@

\subsection{Combinators for expectations}
We propose to use three combinators to set expectations about the
outcome of code examples.

\begin{quote}\small\begin{verbatim}
shouldBe :: (Show a, Eq a) => a -> a -> Assertion
shouldSatisfy :: Show a => a -> (a -> Bool) -> Assertion
shouldReturn :: (Show a, Eq a) => IO a -> a -> Assertion
\end{verbatim}\end{quote}

\subsection{\emph{optional} Automatic discovery of specs}
TBD
